\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-07-28 redaction/dhp_july2017.tex

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 1.052 & 1.044 & 1.041 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%} }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\ 
\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%} }   \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\ 
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
  \label{tab:result_air_rob}
\end{table}%

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends; Applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Air } & {\small (b) Vessel}\\
\includegraphics[width=3in, height=2.5in]{figure5_comme_hummels.pdf}
& \includegraphics[width=3in,height=2.5in]{figure6_comme_hummels.pdf} \\
\end{tabular}
\end{center}
\end{figure}

\textbf{enlever les termes figure 5 et figure 6 des figures}.

>>>>

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 5.2 & 4.4 & 4.1 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%} }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%} }   \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
  \label{tab:result_air_rob}
\end{table}%

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: Applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem Air Freight} & {\small (b) Ad-valorem Vessel Freight}\\
\includegraphics[width=3in, height=2.5in]{figure5_comme_hummels_notitle.pdf}
& \includegraphics[width=3in,height=2.5in]{figure6_comme_hummels_notitle.pdf} \\
\end{tabular}
\end{center}
\end{figure}
